Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-25 content.tex
Second round of processing feedback from reviewers

The second step (Fig.~\ref{fig:pipeline}, 3a)
selects one (or more) inference model(s) $I$ from a set of inference models $I_{1},\dots,I_{n}$. 
We define an experiment $X_{i}$ as the combination of 
an inference model $I_{i}$ and the conditions $C_{i}$ 
to actually use it in the inference step.
As a first example, if the generative model is known and standard,
one can specify this as such.
As a second example, if we want to run only the inference
model that fits best to an alignment from a set of candidates,
one can specify this as well (see section 'Candidate models').

@@

>>>>

The second step (Fig.~\ref{fig:pipeline}, 3a)
selects one or more inference model(s) $I$ from 
a set of standard inference models $I_{1},\dots,I_{n}$.
For example, if the generative model is known and standard,
one can specify an inference model as such.
If the tree model is unknown or non-standard, one can pick
an (assumed) closest standard inference model.
Also, if we want to run only the inference
model that fits best to an alignment from a set of candidates,
one can specify these inference models as 
well (see section 'Candidate models').

@@

Like most phylogenetic experiments, the setup of \verb;pirouette;
is determined by many arbitrary choices. A prime example is the
length of simulated DNA sequence. We predict that the inference error
decreases for longer DNA sequences, but we only investigated this
superficially (see the supplementary materials). The strength
of \verb;pirouette; is, however, to supply a pipeline that is uniform
regardless these choices.
